Dissecting Neural Style Transfer

### 2019-06-01 paper/paper.tex
1

To find more dislocators, let us consider \emph{how to describe a distribution} in general?
The obvious answer is then sample statistics or estimators, like (sample) mean, (sample) standard deviation, 
(sample) skewness, (sample) kurtosis and any moments.
Unfortunately, we found that higher moments are too slow to compute for experiments,
so we ended up with the following (combinations) of sample statistics.
%\begin{enumerate}
%\end{enumerate}

@@

\subsection{Reproducing the original result}

@@

We will also show that other factors, such that the outputs of which functions to derive the style 
losses from are not very essential and somewhat belongs to tuning.

@@

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{MMD}
Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\end{thebibliography}
\end{document}

>>>>

To find more dislocators, let us consider \emph{how to describe a distribution} in general?
The obvious answer is then sample statistics or estimators, like (sample) mean, (sample) standard deviation, 
(sample) skewness, (sample) kurtosis and any moments.
Unfortunately, we found that higher moments too slow to compute for our experiments,
so we ended up with the following (combinations) of sample statistics.
\begin{enumerate}
\item Mean and standard deviation of each type of feature. 
That is, given a $1\times64\times256\times256$ feature map, 
we compute an $1\times64\times2$ array.
Standard deviation is favored over variance because standard deviations 
are supposedly of the same unit of measure as the mean, 
while variances are of a squared unit of measure.
\item Mean, standard deviation and 4th central moment to the power of $1/4$. 
That is, a $1\times64\times3$ array for a $1\times64\times256\times256$ feature map.
\item Mean, standard deviation, 4th central moment to the power of $1/4$, 
and 6th central moment to the power of $1/6$.
\end{enumerate}
We have found by experiment that odd-order moments did not work.
6th central moments were already much slower to compute in practice 
than Gram matrices.
So we could only stop at the 6th moment due to limited experimental capacity.

Unfortunately, straight forward histograms were not computationally feasible.
Although the autograd facility could handle histograms in theory, we were not
able to make histograms work in practice. Similarly, sorting or order statistics
like medians were found to be computationally infeasible in practice.

@@

\subsection{Reproducing the original result}
[[[[Fill the experiment part in demo here to show that we have reproduced result.
Cite the original tutorial]]]] \cite{tut}

We will now show that within the general optimisation framework,
steps other than the Gram matrix, 
such as the outputs of which feature maps to derive the style 
losses from are not very essential.

@@

Now let us see something more interesting.

@@

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{MMD}
Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\bibitem{tut}
Jacq, A. (n.d.). Neural Transfer Using PyTorch (W. Herring, Ed.). Retrieved from https://pytorch.org/tutorials/advanced/neural\_style\_tutorial.html
\end{thebibliography}
\end{document}
